---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`safebrowsing` : retrieve ASN & URL info from Google Safe Browsing

If you're not familiar with Google's "Safe Browing" "service", you should probably [go here](https://www.google.com/transparencyreport/safebrowsing/?hl=en) and read up on it before using this package.

Note also that this is package relies on undocumented APIs and could break if Google changes how they call the underlying XHR requests.

The following functions are implemented:

- `gsb_as_ts`:	Retrieve attack/compromised host time series info for an AS
- `gsb_asinfo`:	Retrive AS info from Google SafeBrowsing
- `gsb_site_status`:	Retrive URL "site status"

### News

- Version  released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/safebrowsing")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(safebrowsing)

# current verison
packageVersion("safebrowsing")

gsb_site_status(c("http://fgcdiesel.cl/encrypted.exe", 
                  "http://rud.is/", "http://dds.ec/"))

gsb_asinfo("largest", 7)

gsb_as_ts("10439")
```

### Test Results

```{r}
library(safebrowsing)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
